### 2015-02-14 docs/report/array_sharing.tex
Fixes in report

If the library is configured to use \(N\) workers then the original data in the \ttarray{} will copied into \(N\) smaller \ttarray{}s. For ideal performance it would be nice to be able to pass a pointer into the array and an amount of elements to process, but since there's no shared memory and element ownership is tranferred to the Web Workers the elements have to be copied to the sub-arrays.

@@

\note{Alternatives \textit{Buffer subarray} and \textit{Constructor} do the same thing in the case of copying an entire \ttarray{}. However, \textit{Constructor} is not a viable alternative for copying part of an array}.

>>>>

If the library is configured to use \(N\) workers then the original data in the \ttarray{} will copied into \(N\) smaller \ttarray{}s. For ideal performance it would be nice to be able to pass a pointer into the array and an amount of elements to process, but since there's no shared memory and element ownership is tranferred to the Web Workers the elements must be copied to the sub-arrays.

@@

\note{Alternatives \textit{Buffer subarray} and \textit{Constructor} do the same thing in the case of copying an entire \ttarray{}. However, \textit{Constructor} is not a viable alternative for copying part of an array}

### 2015-02-14 docs/report/initialization.tex
Fixes in report

As explained in the standard \cite{w3c-ww} \textit{``Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

\subsubsection{Conclusion}
The previous benchmark shows a huge difference between the time required to process a message on a pre-existent Web Worker and that necessary to start Web Worker and process a message. For that reason, we decided to initialize a pool of Web Workers when the library is initialized.

\subsection{High per-instance memory cost}
The first factor makes it important that users can control/limit the amount of web workers that the library instantiates. For that reason the library allows users to specify a maximum amount of workers to be instantiated, and also provide through its API a way to terminate all workers in existance.

\subsection{Maximum amount of workers}
Since the work being done is CPU intensive (i.e.: the workers' goal is not to perform I/O operations), the maximum amount of workers to be created should not be greater than the amount of cores in the machine \(W_{cores}\), otherwise interleaving will start to affect performance. Additionally, considering the necessity of users to control how many workers are created, an upper bound can be specified \(W_{upper bound}\). If no upper bound is specified, the user upper bound for workers is assumed to be infinite (because the user is not providing a restriction). To summarize, the number of workers to be instantiated is:
\[W = min(W_{cores}, W_{upper bound})\]

>>>>

As explained in the Web Workers standard \cite{w3c-ww} \textit{``Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

\subsubsection{Conclusion}
The previous benchmark shows a huge difference between the time required to process a message on a pre-existent Web Worker and that necessary to start Web Worker and process a message. For that reason, we decided to create a pool of Web Workers when the library is initialized.

\subsection{High per-instance memory cost}
The second factor makes it important for users to be able to control/limit the amount of web workers that the library instantiates. For that reason the library allows users to specify a maximum amount of workers to be instantiated, and also provide through its API a way to terminate all workers in existance.

\subsection{Maximum amount of workers}
Since the work being done is CPU intensive (i.e.: the workers' goal is not to perform I/O operations), the maximum amount of workers to be created should not be greater than the amount of cores in the machine \(W_{cores}\), otherwise interleaving would start to affect performance. Additionally, considering the necessity of users to control how many workers are created, an upper bound can be specified \(W_{upper bound}\). If no upper bound is specified, the user upper bound for workers is assumed to be infinite (because the user is not providing a restriction). To summarize, the number of workers to be instantiated is:
\[W = min(W_{cores}, W_{upper bound})\]
